---
title: "Feedback for  `r class_name`"  
date: "`r format(Sys.time(), '%d %B, %Y')`"  
output: html_document  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     # don't show code chunks
  message = FALSE,  # don't show code messages
  warning = FALSE,  # don't show code warnings
  out.width = "75%" # show images at 75% page width
)
library(markr)
```

**Feedback for:** `r student$ID`

**Your marker was:** `r student$marker`

Many thanks for submitting your assignment. Below you will find your personal individual feedback, that only you see, along with more general, generic feedback that the whole class sees.

After reading and reflecting on the comments, you may feel that you want some additional advice from your marker and you can contact them to arrange a meeting or visit them in their student office hours. You can also [make an appointment with a LEADS adviser](https://www.gla.ac.uk/myglasgow/leads/students/) to seek more general advice for writing.

# Your Feedback and FeedForward

## Assessment Criteria

As discussed at the start of term, we assess your work according to the course ILO's and have focused the feedback and feedforward along three assessment marking criteria:

1.  **Quality of the Knowledge and Research**

-   Evidence of depth of knowledge about theory and research, through synthesis of concepts from a range of relevant academic sources, to answer the question.
-   Evidence of depth of research through literature search, appropriately balancing classic and current research.

2.  **Quality of the Comprehension and Evaluation**

-   Ideas are appropriately informed by academic literature, using evidence-based arguments, and giving an insightful response to the set question.
-   Evaluation of the methods, inferences, generalisability, validity and applicability of research throughout.

3.  **Quality of the Academic Communication**

-   Effective communication achieved through well-structured arguments that are coherent and clear, arguments should develop logically, and ideas need to be well linked to supportive evidence.
-   Professionally presented using common psychological conventions. For example, formatting citations and references in APA style, proof reading for spelling and grammatical errors, adhering to word count and formatted for readability.

## Your Individual Feedback

```{r creating-feedback-table, results='asis'}
cols <- list(
  "Criteria 1" = "Knowledge and Research",
  "Criteria 2" = "Critical Evaluation",
  "Criteria 3" = "Academic Communication",
  "LOs" = "Learning Objectives for the Assessment"
)
cats <- list(
  "Excellent" = "**Excellent:** reflect on what went well",
  "Very Good" = "**Very Good:** can be improved by further refining",
  "Good" = "**Good:** though still room for further improvement",
  "Satisfactory" = "**Satisfactory:** ok, but considerable room for improvement",
  "Weak" = "**Weak:** seek advice on how to improve this area",
  "Poor" = "**Poor:** seek advice on how to extensively improve this area",
  "Very Poor" = "**Very Poor:** seek advice on how to extensively improve this area"
)

category_table(student, cols, cats)
```

## Comments from your Marker

`r student$Comment`

## General Class Feedback and FeedForward

Overall the class did a very good job in answering this assignment. Here are some comments we thought would be useful for all students to see and to think about for your next assignment:

* Quirky titles are funny but not that informative. Try to help the future researcher in their search and make your titles informative. 
* Remember that research output is in part a product of the design, so try not to assume one paper as fact.
* Paragraphs work better when they contain one point addressed in detail. Try to avoid too many superficial ideas all collapsed into one paragraph.

