---
title: "markr demo"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, out.width = "75%")
library(markr)
```

## Read data

You can read in all the data from a table format like CSV or Excel, or from a format called YAML. YAML is easier for giving paragraphs of feedback, but the formatting can be a little tricky.

You can also combine data from tabular and YAML files, putting info like student IDs and category marks in a table and paragraphs of feedback in the YAML file.

```{r}
# all data in one table (csv or excel)
marks <- read_marks("marks_fb.csv")

# all data in one YAML file
# marks <- read_marks(yaml = "marks_fb.yml")

# or join data from table and YAML
# marks <- read_marks("marks.csv", "fb.yml", "ID")
```


## Data processing 

You can do some optional further data processing. For example, the marks table had a column called `mark` with the numeric mark, but the feedback template needs a column called `grade` with the letter grade. The function `convert_grades()` defaults to the Glasgow 22-point scale, but you can define your own scale.

```{r}
scale <- data.frame(
  numbers = 4:0,
  letters = c("A", "B", "C", "D", "E")
)
marks$grade <- convert_grades(marks$mark, "letter", scale)
```

## Edit the template

Open the file called `template.Rmd`. It is written in R Markdown. The main thing you need to know at first is how to use hash marks to create titles and subtitles (the more hash marks, the lower-level subtitle) and how to edit inline code.

### Inline code

The information for each individual student will be stored in a list called `student`, and you can reference each column like this: `student$id`. If the column names have spaces or special characters, you can use this format: `student[["ID Number"]]`.

```{r, echo = FALSE}
student <- marks[2, ]
```

To insert information from a column into the text, you use this format: 
<!-- the next line makes this look correct when this document is knit to HTML -->
<code>&grave;r student$marker&grave;</code> 
<!-- the next line shows how it should look in the Rmd file -->
(e.g., `r student$marker`).

You can also reference other variables using inline code, as long as you add them to the `make_feedback()` function later. The title references the variable `class_name`.


### Category Tables

You can display a table of marks for specific criteria by specifying the column names (`cols`) for each criterion and the order that the categories should go in (`cats`).

```{r}
category_table(student, cols = c("KR", "CE", "AC"), cats = 1:4)
```

You can translate abbreviations used in the marking sheet like this:

```{r}
#cols <- c("KR", "CE", "AC") # no translation
cols <- c(
  "KR" = "Knowledge and Research",
  "CE" = "Critical Evaluation",
  "AC" = "Academic Communication"
)

#cats <- 1:4 # no translation
cats <- c(
  "1" = "Needs Work",
  "2" = "Acceptable",
  "3" = "Good",
  "4" = "Outstanding"
)

category_table(student, cols, cats, symbol = "✅")
```

### Make static resources

If each feedback file will have the same image, we can greatly speed up rendering time by creating the image once, saving it to a file, and adding the image to the template using `knitr::include_graphics()`, instead of creating the image in each feedback sheet.

The function `mark_dist()` is provided for your convenience to quickly make grade plots, but you can use any images or plotting functions.

```{r}
# make and save any images that will be in all files
class_plot <- mark_dist(marks, "grade", 
          scale = c("E", "D", "C", "B", "A"))

ggplot2::ggsave("class_plot.png", width = 5, height = 3)
```

## Create feedback files

The following code creates a feedback file for each row in the marks file. It uses the template.Rmd file to create the feedback and saves the files in a folder called "fb" with a filename made from the `ID` and `name` columns of the data. The template uses a variable called `class_name`, so we also need to set that in the arguments.

```{r}
# render the feedback files
make_feedback(
  marks = marks,
  template = "template.Rmd",
  filename = "fb/[ID]_[name].html",
  class_name = "Demo Class"
)
```

## Summary Plots

Plot the mark column with `mark_dist()`. Set the `scale` manually to show all categories in the scale.

```{r}
mark_dist(marks, "mark", scale = 0:5)
```

You can facet the marks by any categorical columns.

```{r}
mark_dist(marks, "grade", facet_by = "question", 
          scale = c("E", "D", "C", "B", "A"))
```

You can also show a plot of individual criteria categories. For example, the demo data has three columns for Knowledge and Research (KR), Critical Evaluation (CE), and Academic Communication (AC). Each criterion is given a category 1-4, which correspond to "Needs Work", "Acceptable", "Good", and "Outstanding". You have to set up the list of columns and categories like for [Category Tables](#Category_Tables) above.

The default plot has the criteria columns across the x-axis and the categories represented by colours. You can facet the plot by any columns in the table.

```{r}
cat_dist(marks, cols, cats, facet_by = "question")
```

Alternatively, you can set `xaxis = "cat"` to display the categories across the x-axis and facet by criteria in addition to any other columns.

```{r}
cat_dist(marks, cols, cats, xaxis = "cat", facet_by = "question")
```

